---
title: "Descriptive Analysis"
author: "GROUP_03"
date: "2024-07-28"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r}
#Import the dataset(Copy of Concrete_Data)

Data<-read.csv("C:\\Users\\User\\OneDrive\\Desktop\\Group_03\\Copy of Concrete_Data.csv")

colnames(Data)<-c("Cement","Blast_Furnace_Slag","Fly_Ash","Water","Superplasticizer","Coarse_Aggregate","Fine_Aggregate","Age_day","Concrete_compressive_strength")

names(Data)

head(Data)
nrow(Data)
###Missing values

print("Total of Missing values")
sum(is.na(Data))

colSums(is.na(Data))


```
This data set has no missing values.


```{r}

##########Descriptive Analysis##########

#################Cement############

##Summary

summary(Data$Cement)
sd(Data$Cement)

##Histogram
hist(Data$Cement,xlab = "Cement",main="Histogram of Cement")


```

```{r}

#################Blast_Furnace_Slag############

##Summary

summary(Data$Blast_Furnace_Slag)
sd(Data$Blast_Furnace_Slag)

##Histogram
hist(Data$Blast_Furnace_Slag,xlab = "Blast_Furnace_Slag",main="Histogram of Blast_Furnace_Slag")




```
```{r}
#################Fly_Ash############

##Summary

summary(Data$Fly_Ash)
sd(Data$Fly_Ash)

##Histogram
hist(Data$Fly_Ash,xlab = "Fly_Ash",main="Histogram of Fly_Ash")



```
```{r}

#################Water############

##Summary

summary(Data$Water)
sd(Data$Water)

##Histogram
hist(Data$Water,xlab = "Water",main="Histogram of Water")


```

```{r}

###############Superplasticizer############

##Summary

summary(Data$Superplasticizer)
sd(Data$Superplasticizer)

##Histogram
hist(Data$Superplasticizer,xlab = "Superplasticizer",main="Histogram of Superplasticizer")


```

```{r}
###############Coarse_Aggregate############

##Summary

summary(Data$Coarse_Aggregate)
sd(Data$Coarse_Aggregate)

##Histogram
hist(Data$Coarse_Aggregate,xlab = "Coarse_Aggregate",main="Histogram of Coarse_Aggregate")



```
```{r}
###############Fine_Aggregate############

##Summary

summary(Data$Fine_Aggregate)
sd(Data$Fine_Aggregate)

##Histogram
hist(Data$Fine_Aggregate,xlab = "Fine_Aggregate",main="Histogram of Fine_Aggregate")



```

```{r}
###############`Age_day`############

##Summary

summary(Data$Age_day)
sd(Data$Age_day)

##Histogram
hist(Data$Age_day,xlab = "Age_(day)",main="Histogram of Age_(day)")



```

```{r}
###############Concrete_compressive_strength############

##Summary

summary(Data$Concrete_compressive_strength)
sd(Data$Concrete_compressive_strength)

##Histogram
hist(Data$Concrete_compressive_strength,xlab = "Concrete_compressive_strength",main="Histogram of Concrete_compressive_strength")



```
```{r}
####Outliers


# create detect outlier function
detect_outlier <- function(x) {
  
  # calculate first quantile
  Quantile1 <- quantile(x, probs=.25)
  
  # calculate third quantile
  Quantile3 <- quantile(x, probs=.75)
  
  # calculate interquartile range
  IQR = Quantile3 - Quantile1
  
  # return true or false
  x > Quantile3 + (IQR * 1.5) | x < Quantile1 - (IQR * 1.5)
}

# create remove outlier function
remove_outlier <- function(dataframe, columns = names(dataframe)) {
  
  # for loop to traverse in columns vector
  for (col in columns) {
    
    # remove observation if it satisfies outlier function
    dataframe <- dataframe[!detect_outlier(dataframe[[col]]), ]
  }
  
  print("Remove outliers")
  print(dataframe)
}

cleaned_data_1<-remove_outlier(Data, c('Cement','Blast_Furnace_Slag','Fly_Ash','Water','Superplasticizer','Coarse_Aggregate','Fine_Aggregate','Age_day','Concrete_compressive_strength'))

cleaned_data_2<-remove_outlier(cleaned_data_1, c('Cement','Blast_Furnace_Slag','Fly_Ash','Water','Superplasticizer','Coarse_Aggregate','Fine_Aggregate','Age_day','Concrete_compressive_strength'))

cleaned_data<-remove_outlier(cleaned_data_2, c('Cement','Blast_Furnace_Slag','Fly_Ash','Water','Superplasticizer','Coarse_Aggregate','Fine_Aggregate','Age_day','Concrete_compressive_strength'))

nrow(cleaned_data)

```
##########Boxplots after removing Outliers

```{r}
#Cement
##Boxplot
boxplot(cleaned_data$Cement,ylab="Cement",main="Boxplot of Cement")

```



```{r}


#Blast_Furnace_Slag
##Boxplot
boxplot(cleaned_data$Blast_Furnace_Slag,ylab="Blast_Furnace_Slag",main="Boxplot of Blast_Furnace_Slag")



```

```{r}
##Fly_Ash
##Boxplot
boxplot(cleaned_data$Fly_Ash,ylab="Fly_Ash",main="Boxplot of Fly_Ash")


```
```{r}
#Water
##Boxplot
boxplot(cleaned_data$Water,ylab="Water",main="Boxplot of Water")


```

```{r}
#Superplasticizer
##Boxplot
boxplot(cleaned_data$Superplasticizer,ylab="Superplasticizer",main="Boxplot of Superplasticizer")
```

```{r}
##Coarse_Aggregate
##Boxplot
boxplot(cleaned_data$Coarse_Aggregate,ylab="Coarse_Aggregate",main="Boxplot of Coarse_Aggregate")
```


```{r}
##Fine_Aggregate
##Boxplot
boxplot(cleaned_data$Fine_Aggregate,ylab="Fine_Aggregate",main="Boxplot of Fine_Aggregate")
```
```{r}
#Age_(day)
##Boxplot
boxplot(cleaned_data$Age_day,ylab="`Age_(day)`",main="Boxplot of `Age_(day)`")

```
```{r}
#Concrete_compressive_strength
##Boxplot
boxplot(cleaned_data$Concrete_compressive_strength,ylab="Concrete_compressive_strength",main="Boxplot of Concrete_compressive_strength")
```




```{r}
###This is our cleaned dataset


head(cleaned_data)

nrow(cleaned_data)

```

---
title: "All"
author: "GROUP_03"
date: "2024-08-05"
output:
  word_document: default
  html_document: default
---

```{r}
#####Install packages#######

library(dplyr)
library(tidyr)
library(MASS)
library(Metrics)
library(ISLR)
library(leaps)
library(ggplot2)
library(quantmod)
library(corrplot)
library(caTools)
library(car)


###Scatter plots
pairs(cleaned_data)

###Correlations
cor(cleaned_data)


###All preductors

lm_0<-lm(Concrete_compressive_strength~.,data = cleaned_data)
summary(lm_0)

```
##Interpretation



```{r}
###Anova test

anova(lm_0)
```
##Interpretation


```{r}
########Model Selection###########

######Forward stepwise Selection#########
fit_frwd<-regsubsets(Concrete_compressive_strength~ .,data = cleaned_data,nvmax = 8,method = "forward")
frwd_summary<-summary(fit_frwd)
frwd_summary

```
##Interpretation


```{r}
##########Find Adj R^2,Cp,BIC,RSS values
criterion<-data.frame(model=1:8,
                      Adj.R2=(frwd_summary$adjr2),
                      Cp=(frwd_summary$cp),
                      BIC=(frwd_summary$bic),
                      RSS=(frwd_summary$rss))
##Add MS_Res
n<-nrow(cleaned_data)

criterion$MS_Res<-criterion$RSS/(n-criterion$model-1)


##Standardize
criterion_std<-cbind(model=criterion$model,scale(criterion[,-1]))
criterion_std<-as.data.frame(criterion_std)

###Values
criterion_std

###Graphically
ggplot(criterion_std,aes(model))+
  geom_line(aes(y=Adj.R2,colour="Adj.R2"))+
  geom_line(aes(y=Cp,colour="Cp"))+
  geom_line(aes(y=BIC,colour="BIC"))+
  geom_line(aes(y=RSS,colour="RSS"))+
  geom_line(aes(y=MS_Res,colour="MS_Res"))+
  theme_minimal()
```
###Interpretation
model 6 is better model



```{r}
##coefficients

coef(fit_frwd,6)

model_1<-lm(Concrete_compressive_strength~Cement+Blast_Furnace_Slag+Fly_Ash+Water+Superplasticizer+Age_day,data = cleaned_data)
summary(model_1)

```
##Interpretation
###############With Leverage points
```{r}
##With Leverage points
##Check for Homoscedasticity using residuals vs fitted values plot. 

plot(model_1,which = 1,col=c("blue"))

```
```{r}
##With Leverage points
##Check for Independent or dependent using residuals vs Observation value plot.

res <- data.frame(res = resid(model_1))
avp <- cbind(cleaned_data, res)
plot(1:nrow(avp), avp$res,
 main = "Residuals vs. Observation",
 xlab = "Observations",
 ylab = "Residual",
 col = "blue") 
```
```{r}

##With Leverage points
###Check the normality of residuals.(using QQ plot)
plot(model_1,which = 2,col=c("black"))
```
```{r}

##With Leverage points
###Check the residual vs Leverage.
plot(model_1,which = 5,col=c("blue"))
```






###############Without Leverage points

```{r}
##Check the leverage points


leverage<-hatvalues(model_1)
high_leverage<-which(leverage>2*(6+1)/nrow(cleaned_data))
high_leverage

cleaned_dataset <- cleaned_data[-high_leverage, ]



nrow(cleaned_dataset)


```

```{r}

better_model<-lm(Concrete_compressive_strength~Cement+Blast_Furnace_Slag+Fly_Ash+Water+Superplasticizer+Age_day,data = cleaned_dataset)
summary(better_model)


```





```{r}
###Model diagnostics

##Without Leverage points
##Check the linearity using scatter plots.

#Concrete_compressive_strength vs Cement
plot(Concrete_compressive_strength~Cement,data = cleaned_dataset,main="Concrete_compressive_strength vs Cement")


#Concrete_compressive_strength vs Blast_Furnace_Slag
plot(Concrete_compressive_strength~Blast_Furnace_Slag,data =cleaned_dataset,main="Concrete_compressive_strength vs Blast_Furnace_Slag")


#Concrete_compressive_strength vs Fly_Ash
plot(Concrete_compressive_strength~Fly_Ash,data = cleaned_dataset,main="Concrete_compressive_strength vs Fly_Ash")


#Concrete_compressive_strength vs Water
plot(Concrete_compressive_strength~Water,data = cleaned_dataset,main="Concrete_compressive_strength vs Water")


#Concrete_compressive_strength vs Superplasticizer
plot(Concrete_compressive_strength~Superplasticizer,data = cleaned_dataset,main="Concrete_compressive_strength vs Superplasticizer")


#Concrete_compressive_strength vs Age_day
plot(Concrete_compressive_strength~Age_day,data = cleaned_dataset,main="Concrete_compressive_strength vs Age_day")

```



```{r}
##Without Leverage points
##Check for Homoscedasticity using residuals vs fitted values plot. 

plot(better_model,which = 1,col=c("blue"))
```
It seems that the fitted values are contain the constant variance. Then the homoscedasticity property hold. 

```{r}

##Without Leverage points
##Check for Independent or dependent using residuals vs Observation value plot.

res <- data.frame(res = resid(better_model))
avp <- cbind(cleaned_dataset, res)
plot(1:nrow(avp), avp$res,
 main = "Residuals vs. Observation",
 xlab = "Observations",
 ylab = "Residual",
 col = "blue") 

```
It seems that the  errors are uncorrelated. 

```{r}

##Without Leverage points
###Check the normality of residuals.(using QQ plot)
plot(better_model,which = 2,col=c("black"))


```
The maximum points fall approximately along the reference line. Therefore the residuals are normally 
distributed

##Interpretation

```{r}
##Without Leverage points
###Check the residual vs Leverage.
plot(better_model,which = 5,col=c("blue"))
```




```{r}
##########Multicollinearity#############

vif_values<-vif(better_model)
vif_values

```
```{r}
###Shapiro test

```




